### 2022-03-11 paper/localpsf.tex
impulse response moments section in intro

\subsection{Local mean-displacement invariance}
\label{eq:local_mean_displacement_invariance}

Let $x$ and $x'$ be points in $\Omega$ that are ``close'' to each other, and consider the following three approximations, ordered by increasing level of sophistication:
\begin{align}
\phi_x(y) &\approx \phi_{x'}(y) \label{eq:translate1}\\
\phi_x(y) &\approx \phi_{x'}(y-x+x') \label{eq:translate2}\\
\phi_x(y) &\approx \phi_{x'}\left(y-\mu(x)+\mu(x')\right). \label{eq:translate3}
\end{align}
Approximation \eqref{eq:translate1} says that $\phi_x$ can be approximated by $\phi_{x'}$ when $x$ and $x'$ are close. 
%This approximation follows from the assumption that $\Phi$ is smooth. 
Operators satisfying \eqref{eq:translate1} can be well-approximated via low-rank interpolative factorization of $\Phi$.
% of the form
%\begin{equation}
%	\label{eq:low_rank_interpolation}
%	\Phi(y,x) \approx \sum_{i=1}^r w_i(x) \phi_{x_i}(y)
%\end{equation}
%where $\phi_{x_i}$ are known impulse responses at a collection of points $x_i$ scattered throughout $\Omega$, and $w_i$ are smooth weighting functions that interpolate the $\phi_{x_i}$. 
%In problems of practical interest, \eqref{eq:translate1} typically holds \emph{asymptotically} in the limit as $x'$ approaches $x$. 
However, 
%even if $\Phi$ is smooth (which is typically the case asymptotically),
%the relevant Lipschitz constant for continuity, and hence 
the required rank in the low rank approximation can be large, which makes algorithms based on assumption \eqref{eq:translate1} computationally expensive. This is the case, for example, for Hessians in PDE constrained inverse problems with highly informative data, as discussed in Section \ref{sec:PDE_hessian_motivation}. 
%As the data become more informative, typically the ``mass'' of $\Phi(y,x)$ concentrates nearer and nearer to the ``diagonal'' $y=x$, the Lipschitz constant increases, and the required rank in the approximation increases.
%Moreover, if $\Aop$ is numerically low rank, then one would typically use more accurate and robust matrix-free methods for forming low-rank approximations, such as randomized SVD or Lanczos.

@@

The impulse response $\impulseresponse_x$ may be interpreted as a scaled probability distribution because of the non-negative impulse response property. Let $\spatialvol:\Omega \rightarrow \mathbb{R}$,
\begin{equation*}
\spatialvol(x) := \int_\Omega \impulseresponse_x(y) dy
\end{equation*}
denote the spatially varying scaling factor (the ``volume'' of $\impulseresponse_x$), let 
\begin{equation}
\label{eq:scaled_impulse_response}
\widehat{\impulseresponse}_x := \impulseresponse_x / \spatialvol(x)
\end{equation}
denote the normalized version of $\impulseresponse_x$, and let $\mu:\Omega \rightarrow \mathbb{R}^d$, $\Sigma:\Omega \rightarrow \mathbb{R}^{d \times d},$
\begin{equation*}
\spatialmean(x) := \mathbb{E}(\widehat{\impulseresponse}_x), \qquad
\spatialcov(x) := \Var(\widehat{\impulseresponse}_x),
\end{equation*}
denote the spatially varying mean and covariance of $\widehat{\impulseresponse}_x$, respectively. In Section \ref{eq:mean_and_covariance_estimation} we will see that it is possible to compute $V(x)$, $\mu(x)$, and $\Sigma(x)$ for all $x \in \Omega$ simultaneously, via a procedure that involves applying $\Aop^T$ to a small number of polynomial functions (three functions if $\gdim=1$, six if $\gdim=2$, ten if $\gdim=3$).

Since a probability distribution concentrates within a small number of standard deviations of its mean, knowing $\mu(x)$ and $\Sigma(x)$ permits us to form an ellipsoid shaped estimate for the support of $\phi_x$, \emph{without} computing $\phi_x$. This allows us to compute large numbers of impulse responses, $\impulseresponse_{x_i}$, in ``batches.'' We compute one batch of $\impulseresponse_{x_i}$'s by applying $\Aop$ to a weighted sum of point sources (Dirac comb) associated with a collection of points $x_i$ scattered throughout $\Omega$. The batch of points $x_i$ are chosen via a greedy ellipsoid packing algorithm so that the support of $\impulseresponse_{x_i}$ and the support of $\impulseresponse_{x_j}$ do not overlap (or do not overlap much) if $i \neq j$. Because these supports do not overlap, we can post-process the response of $\Aop$ to the Dirac comb to recover the functions $\impulseresponse_{x_i}$ associated with all points $x_i$ in the batch---with one application of $\Aop$, we recover many $\impulseresponse_{x_i}$. This is illustrated in Figure FIG. The process is repeated to get more batches, until a desired number of impulse responses is reached.

@@

The ability to rapidly evaluate approximate kernel entries $\Phi(y,x)$ allows us to construct an H-matrix approximation, $\boldsymbol{\Phi}_H$, of $\Phi$, using the conventional adaptive cross H-matrix construction method. In this method, one forms low-rank approximations of off-diagonal blocks of the matrix by sampling rows and columns of those blocks \cite{HACA}. We then use H-matrix methods to convert $\boldsymbol{\Phi}_H$ into an H-matrix approximation of $\Aop$, denoted $\mathbf{A}_H$. Schematically the overall H-matrix approximation proceeds as follows:
\begin{equation*}
\Aop \longrightarrow V, \mu, \Sigma \longrightarrow \{\impulseresponse_{x_i}\}_{i=1}^r \longrightarrow \boldsymbol{\Phi}_H \longrightarrow \mathbf{A}_H.
\end{equation*}
One may use H-matrix methods to perform further useful linear algebra operations involving $\mathbf{A}_H$, including matrix-matrix addition, matrix-matrix multiplication, matrix-vector products, matrix factorization, and matrix inversion. These H-matrix methods are fast and scale well to large problems. WHY DO THESE OPERATIONS: KRYLOV SOLVERS, SAMPLING STRATEGIES, CAN'T DO WITH A.

@@

In general, product-convolution approximations take the form shown in \eqref{eq:product_convolution}, but $\convkernel_i$ and $w_i$ may be arbitrary functions. Product-convolution approximations have been used in a wide variety of fields going back several decades \cite{PRODCONVLIST}.
For background on product-convolution approximations, we recommend reading the following papers: \cite{PRODCONVGOOD}.

We build upon the class of product convolution approximations in which the functions, $\convkernel_i$, are impulse responses of $\Aop$ to point sources at a collection of points $x_i$ \cite{PRODCONVLIST}. A popular choice for methods in this class is to choose the points $x_i$ to be nodes in a regular grid, and interpolate the functions $\convkernel_i$ with piecewise linear interpolation \cite{NAGY}, or splines \cite{PRODCONVSPLINES}. With a regular grid, a large number of points $x_i$ is typically required to achieve an accurate product-convolution approximation. In our previous work, we reduced the computational cost by starting with a coarse grid of points $x_i$, then adaptively refining the grid in the regions where the error in the approximation is large \cite{PRODCONVMYPAPER}. But even with adaptive refinement, many matrix vector products with $\Aop$ may be required. In this paper, rather than using adaptive refinement, we instead reduce the computational cost by picking points $x_i$ such that many $\convkernel_i$ are computed with each matrix vector product.

Our method of estimating the support of the functions $\convkernel_i$ was inspired by resolution analysis in seismic imaging \cite{RESOLUTION}. In resolution analysis, $\Aop$ is the Hessian for a seismic inverse problem, and the width of $\convkernel_p$ is used to estimate of the minimum length scale on which features of the parameter can be inferred near the point $p$. If the width of $\convkernel_p$ is ten meters, then features of the parameter near $p$ can be accurately inferred from data if those features are larger than roughly ten meters in size. In \cite{RESOLUTION}, the width of $\convkernel_p$ is estimated to be the local autocorrelation length of the function $\Aop^T \zeta$ near $p$, where $\zeta$ is a random noise funtion. In this paper, rather than probing $\Aop^T$ with random noise functions, we use polynomial functions. Our method estimates the support of $\convkernel_p$ more accurately and reliably than resolution analysis, but our method requires that $\Aop$ has a positive integral kernel, while the resolution analysis method does not have this requirement.

@@

	\Input{Finite set of candidate points $P\subset \Omega$, \\spatialmean $\spatialmean(x)$ and covariance $\spatialcov(x)$, \\domain boundary information $\partial \Omega$, \\previous sample point batches $\pointbatch_1, \dots, \pointbatch_{k-1}$}
	\Output{Batch of new sample points $\pointbatch_k$}

@@

Let $u_h \in V_h$ and $v_h \in V_h$, and let $\bm{u}$ and $\bm{v}$ be the coefficient vectors for $u_h$ and $v_h$, respectively, with respect to the finite element basis $\febasis_1, \dots, \febasis_\fedim$. I.e., 
\begin{equation}
\label{eq:fem_coeff_basis}
u_h(x) = \sum_{i=1}^\fedim \bm{u}_i \febasis_i(x),
\end{equation}
and similar for $v_h$. Replacing $\Aker$ with $\widetilde{\Phi}^h$ within the definition of $\Aop$ in \eqref{eq:kernel_representation}, then performing straightforward but tedious algebraic manipulations, yields the following approximation:
\begin{equation}
	\label{eq:kernel_representation_pcmesh}
	(\Aop u_h)(v_h) \approx \int_\Omega \int_\Omega v_h(y) \Phi^h(y,x) u_h(x) dx dy
	= \bm{v}^T \bm{M} \mathbf{\Phi} \bm{M} \bm{u}.
\end{equation}
%While $\Aop$ is well-defined as a mapping $L^2(\Omega) \rightarrow L^2(\Omega)'$, we are interested in the restriction of $\Aop$ to functions in the finite element space. 
where $\mathbf{\Phi} \in \mathbb{R}^{\fedim \times \fedim}$ is the following matrix of approximate kernel entries:
\begin{equation}
	\label{eq:Akerpcmat_entries}
	\mathbf{\Phi}_{ij} := \widetilde{\Phi}(p_i, p_j),
\end{equation}
and $\bm{M} \in \mathbb{R}^{\fedim \times \fedim}$ is the finite element mass matrix which has entries
\begin{equation*}
\bm{M}_{ij}=\int_\Omega \febasis_i(x) \febasis_j(x) dx.
\end{equation*}
%Using \eqref{eq:defn_of_Akerpcmesh}, \eqref{eq:kernel_representation_pcmesh}, \eqref{eq:fem_coeff_basis}, and \eqref{eq:Akerpcmat_entries}, the definition of the mass matrix, and performing algebraic manipulations, it is straightforward but tedious to show that
%\begin{equation*}
%	\left(\AopPcMesh u_h \right)(v_h) = \bm{v}^T \bm{M} \AkerPcMat \bm{M} \bm{u}.
%\end{equation*}
The finite element matrix representation of of our approximation of $\Aop$ is therefore given by
\begin{equation}
	\label{eq:Amatpc_defn}
	\mathbf{A} = \bm{M} \mathbf{\Phi} \bm{M}.
\end{equation}

@@

Let $\overline{\Omega}$ be the closure of $\Omega$, and let $C(\overline{\Omega})$ be the space of continuous functions mapping $\overline{\Omega}\rightarrow \mathbb{R}$. The action of $\Aop$ is extended to distributions $\genericdistribution:C\left(\overline{\Omega}\right) \rightarrow \mathbb{R}$ via the formula
\begin{equation*}
	\left(\Aop \genericdistribution^*\right)(v) := \int_\Omega v(y) \genericdistribution\left(A(y, \cdot)\right) dy, 
\end{equation*}
where $A(y,\cdot)$ is the function $x \mapsto A(y,x)$. This is derived formally as follows:
\begin{align*}
	\left(\Aop \genericdistribution^*\right)(v) &= \int_\Omega \int_\Omega v(y) A(y,x) \textrm{``} \genericdistribution(x) \textrm{''} dx dy \\
	&= \int_\Omega v(y) \int_\Omega A(y,x) \textrm{``} \genericdistribution(x) \textrm{''} dx \\
	&= \int_\Omega v(y) \genericdistribution\left(A(y,\cdot)\right) dx.
\end{align*}
For example, the delta distribution $\delta_x$ is defined by $\delta_x(v) = v(x)$, and the action of $\Aop$ on $\delta_x$ is given by
\begin{equation}
	\label{eq:appendix_impulse_response}
	\left(\Aop \delta_x^*\right)(v)	= \int_\Omega v(y) A(y,x) dy.
\end{equation}
Recall that the impulse response of $\Aop$ to $\delta_x$, denoted $\impulseresponse_x$, is the Riesz representation of $\Aop \delta_x^*$. From \eqref{eq:appendix_impulse_response} and the definition of the Riesz representation, we have $\impulseresponse_x = A(~\cdot~,x)$. That is, $\impulseresponse_x$ is the function $y \mapsto A(y,x)$.

>>>>

\subsection{Impulse response moments}
\label{sec:intromoments}

The impulse response $\impulseresponse_x$ may be interpreted as a scaled probability distribution because of the non-negative impulse response property. Let $\spatialvol:\Omega \rightarrow \mathbb{R}$,
\begin{equation*}
\spatialvol(x) := \int_\Omega \impulseresponse_x(y) dy
\end{equation*}
denote the spatially varying scaling factor (the ``volume'' of $\impulseresponse_x$), let 
\begin{equation}
\label{eq:scaled_impulse_response}
\widehat{\impulseresponse}_x := \impulseresponse_x / \spatialvol(x)
\end{equation}
denote the normalized version of $\impulseresponse_x$, and let $\mu:\Omega \rightarrow \mathbb{R}^d$, $\Sigma:\Omega \rightarrow \mathbb{R}^{d \times d},$
\begin{equation*}
\spatialmean(x) := \mathbb{E}(\widehat{\impulseresponse}_x), \qquad
\spatialcov(x) := \Var(\widehat{\impulseresponse}_x),
\end{equation*}
denote the spatially varying mean and covariance of $\widehat{\impulseresponse}_x$, respectively.

\subsection{Volume preconditioned local mean-displacement invariance}
\label{eq:local_mean_displacement_invariance}

Let $x$ and $x'$ be points in $\Omega$ that are ``close'' to each other, and consider the following four approximations, ordered by increasing level of sophistication:
\begin{align}
\phi_x(y) &\approx \phi_{x'}(y) \label{eq:translate1}\\
\phi_x(y) &\approx \phi_{x'}(y-x+x') \label{eq:translate2}\\
\phi_x(y) &\approx \phi_{x'}\left(y-\mu(x)+\mu(x')\right) \label{eq:translate3}\\
\frac{\phi_x(y)}{V(x)} &\approx \frac{\phi_{x'}\left(y-\mu(x)+\mu(x')\right)}{V(x')}. \label{eq:translate4}
\end{align}
Approximation \eqref{eq:translate1} says that $\phi_x$ can be approximated by $\phi_{x'}$ when $x$ and $x'$ are close. 
%This approximation follows from the assumption that $\Phi$ is smooth. 
Operators satisfying \eqref{eq:translate1} can be well-approximated via low-rank interpolative factorization/Nystrom approximation of $\Phi$ \cite{CUR,NYSTROM}.
% of the form
%\begin{equation}
%	\label{eq:low_rank_interpolation}
%	\Phi(y,x) \approx \sum_{i=1}^r w_i(x) \phi_{x_i}(y)
%\end{equation}
%where $\phi_{x_i}$ are known impulse responses at a collection of points $x_i$ scattered throughout $\Omega$, and $w_i$ are smooth weighting functions that interpolate the $\phi_{x_i}$. 
%In problems of practical interest, \eqref{eq:translate1} typically holds \emph{asymptotically} in the limit as $x'$ approaches $x$. 
However, 
%even if $\Phi$ is smooth (which is typically the case asymptotically),
%the relevant Lipschitz constant for continuity, and hence 
the required rank in the low rank approximation can be large, which makes algorithms based on assumption \eqref{eq:translate1} computationally expensive. This is the case for Hessians in PDE constrained inverse problems with highly informative data, as discussed in Section \ref{sec:PDE_hessian_motivation}. 
%As the data become more informative, typically the ``mass'' of $\Phi(y,x)$ concentrates nearer and nearer to the ``diagonal'' $y=x$, the Lipschitz constant increases, and the required rank in the approximation increases.
%Moreover, if $\Aop$ is numerically low rank, then one would typically use more accurate and robust matrix-free methods for forming low-rank approximations, such as randomized SVD or Lanczos.

@@

In Section \ref{eq:mean_and_covariance_estimation} we will see that it is possible to compute $V(x)$, $\mu(x)$, and $\Sigma(x)$ for all $x \in \Omega$ simultaneously, via a procedure that involves applying $\Aop^T$ to a small number of polynomial functions (three functions if $\gdim=1$, six if $\gdim=2$, ten if $\gdim=3$). Since a probability distribution concentrates within a small number of standard deviations of its mean, knowing $\mu(x)$ and $\Sigma(x)$ permits us to form an ellipsoid shaped estimate for the support of $\phi_x$, \emph{without} computing $\phi_x$. This allows us to compute large numbers of impulse responses, $\impulseresponse_{x_i}$, in ``batches.'' We compute one batch of $\impulseresponse_{x_i}$'s by applying $\Aop$ to a weighted sum of point sources (Dirac comb) associated with a collection of points $x_i$ scattered throughout $\Omega$. The batch of points $x_i$ are chosen via a greedy ellipsoid packing algorithm so that the support of $\impulseresponse_{x_i}$ and the support of $\impulseresponse_{x_j}$ do not overlap (or do not overlap much) if $i \neq j$. Because these supports do not overlap, we can post-process the response of $\Aop$ to the Dirac comb to recover the functions $\impulseresponse_{x_i}$ associated with all points $x_i$ in the batch---with one application of $\Aop$, we recover many $\impulseresponse_{x_i}$. This is illustrated in Figure FIG. The process is repeated to get more batches, until a desired number of impulse responses is reached.

@@

The ability to rapidly evaluate approximate kernel entries $\Phi(y,x)$ allows us to construct an H-matrix approximation, $\boldsymbol{\Phi}_H$, of $\Phi$, using the conventional adaptive cross H-matrix construction method. In this method, one forms low-rank approximations of off-diagonal blocks of the matrix by sampling rows and columns of those blocks \cite{HACA}. We then use H-matrix methods to convert $\boldsymbol{\Phi}_H$ into an H-matrix approximation of $\Aop$, denoted $\mathbf{A}_H$. Schematically the overall H-matrix approximation proceeds as follows:
\begin{equation*}
\Aop \longrightarrow V, \mu, \Sigma \longrightarrow \{x_i\}_{i=1}^r \longrightarrow \{\impulseresponse_{x_i}\}_{i=1}^r \longrightarrow \boldsymbol{\Phi}_H \longrightarrow \mathbf{A}_H.
\end{equation*}
One may use H-matrix methods to perform further useful linear algebra operations involving $\mathbf{A}_H$, including matrix-matrix addition, matrix-matrix multiplication, matrix-vector products, matrix factorization, and matrix inversion. These H-matrix methods are fast and scale well to large problems. WHY DO THESE OPERATIONS: KRYLOV SOLVERS, SAMPLING STRATEGIES, CAN'T DO WITH A.

@@

%In general, product-convolution approximations take the form shown in \eqref{eq:product_convolution}, but $\convkernel_i$ and $w_i$ may be arbitrary functions.
Product-convolution approximations have been used in a wide variety of fields going back several decades \cite{PRODCONVLIST}.
For background on product-convolution approximations, we recommend reading the following papers: \cite{PRODCONVGOOD}. We build upon the class of product convolution approximations in which the convolution kernels are shifted impulse responses of $\Aop$ to point sources at a collection of points $x_i$ \cite{PRODCONVLIST}. A popular choice for methods in this class is to choose the points $x_i$ to be nodes in a regular grid, and interpolate the convolution operators with piecewise linear interpolation \cite{NAGY}, or splines \cite{PRODCONVSPLINES}. With a regular grid, a large number of points $x_i$ is typically required to achieve an accurate product-convolution approximation. In our previous work, we reduced the computational cost by starting with a coarse grid of points $x_i$, then adaptively refining the grid in the regions where the error in the approximation is large \cite{PRODCONVMYPAPER}. But even with adaptive refinement, many matrix vector products with $\Aop$ may be required. In this paper, rather than using adaptive refinement, we instead reduce the computational cost by picking points $x_i$ such that many $\convkernel_i$ are computed with each matrix vector product.

Our method of estimating the support of the impulse responses was inspired by resolution analysis in seismic imaging \cite{RESOLUTION}. In resolution analysis, $\Aop$ is the Hessian for a seismic inverse problem, and the width of $\phi_p$ is used to estimate of the minimum length scale on which features of the parameter can be inferred near the point $p$. If the width of $\phi_p$ is ten meters, then features of the parameter near $p$ can be accurately inferred from data if those features are larger than roughly ten meters in size. In \cite{RESOLUTION}, the width of $\phi_p$ is estimated to be the local autocorrelation length of the function $\Aop^T \zeta$ near $p$, where $\zeta$ is a random noise funtion. In this paper, rather than probing $\Aop^T$ with random noise functions, we use polynomial functions. Our method estimates the support of $\phi_p$ more accurately and reliably than resolution analysis, but our method requires that $\Aop$ has a positive integral kernel, while the resolution analysis method does not have this requirement.

@@

	\Input{Finite set of candidate points $P\subset \Omega$, \\spatially varying mean $\spatialmean(x)$ and covariance $\spatialcov(x)$, \\domain boundary information $\partial \Omega$, \\previous sample point batches $\pointbatch_1, \dots, \pointbatch_{k-1}$}
	\Output{Batch of new sample points $\pointbatch_k$}

@@

Let $u_h \in V_h$ and $v_h \in V_h$, and let $\bm{u}$ and $\bm{v}$ be the coefficient vectors for $u_h$ and $v_h$, respectively, with respect to the finite element basis $\febasis_1, \dots, \febasis_\fedim$. I.e., 
\begin{equation}
\label{eq:fem_coeff_basis}
u_h(x) = \sum_{i=1}^\fedim \bm{u}_i \febasis_i(x),
\end{equation}
and similar for $v_h$. Replacing $\Aker$ with $\widetilde{\Phi}^h$ within the definition of $\Aop$ in \eqref{eq:kernel_representation}, then performing straightforward but tedious algebraic manipulations, yields the following approximation:
\begin{equation}
	\label{eq:kernel_representation_pcmesh}
	(\Aop u_h)(v_h) \approx \int_\Omega \int_\Omega v_h(y) \Phi^h(y,x) u_h(x) dx dy
	= \bm{v}^T \bm{M} \mathbf{\Phi} \bm{M} \bm{u}.
\end{equation}
%While $\Aop$ is well-defined as a mapping $L^2(\Omega) \rightarrow L^2(\Omega)'$, we are interested in the restriction of $\Aop$ to functions in the finite element space. 
where $\mathbf{\Phi} \in \mathbb{R}^{\fedim \times \fedim}$ is the following matrix of approximate kernel entries:
\begin{equation}
	\label{eq:Akerpcmat_entries}
	\mathbf{\Phi}_{ij} := \widetilde{\Phi}(p_i, p_j),
\end{equation}
and $\bm{M} \in \mathbb{R}^{\fedim \times \fedim}$ is the finite element mass matrix which has entries
\begin{equation*}
\bm{M}_{ij}=\int_\Omega \febasis_i(x) \febasis_j(x) dx.
\end{equation*}
%Using \eqref{eq:defn_of_Akerpcmesh}, \eqref{eq:kernel_representation_pcmesh}, \eqref{eq:fem_coeff_basis}, and \eqref{eq:Akerpcmat_entries}, the definition of the mass matrix, and performing algebraic manipulations, it is straightforward but tedious to show that
%\begin{equation*}
%	\left(\AopPcMesh u_h \right)(v_h) = \bm{v}^T \bm{M} \AkerPcMat \bm{M} \bm{u}.
%\end{equation*}
The finite element matrix representation of our approximation of $\Aop$ is therefore given by
\begin{equation}
	\label{eq:Amatpc_defn}
	\mathbf{A} = \bm{M} \mathbf{\Phi} \bm{M}.
\end{equation}

@@

%Let $\overline{\Omega}$ be the closure of $\Omega$, and let $C(\overline{\Omega})$ be the space of continuous functions mapping $\overline{\Omega}\rightarrow \mathbb{R}$. 
The action of $\Aop$ is extended to distributions $\rho$
%$\genericdistribution:C\left(\overline{\Omega}\right) \rightarrow \mathbb{R}$ 
via the formula
\begin{equation*}
	\left(\Aop \genericdistribution^*\right)(v) := \int_\Omega v(y) \genericdistribution\left(\Phi(y, \cdot)\right) dy, 
\end{equation*}
where $\Phi(y,\cdot)$ is the function $x \mapsto \Phi(y,x)$. This is derived formally as follows:
\begin{align*}
	\left(\Aop \genericdistribution^*\right)(v) &= \int_\Omega \int_\Omega v(y) \Phi(y,x) \textrm{``} \genericdistribution(x) \textrm{''} dx dy \\
	&= \int_\Omega v(y) \int_\Omega \Phi(y,x) \textrm{``} \genericdistribution(x) \textrm{''} dx \\
	&= \int_\Omega v(y) \genericdistribution\left(\Phi(y,\cdot)\right) dx.
\end{align*}
For example, the delta distribution $\delta_x$ is defined by $\delta_x(v) = v(x)$, and the action of $\Aop$ on $\delta_x$ is given by
\begin{equation}
	\label{eq:appendix_impulse_response}
	\left(\Aop \delta_x^*\right)(v)	= \int_\Omega v(y) \Phi(y,x) dy.
\end{equation}
Recall that the impulse response of $\Aop$ to $\delta_x$, denoted $\impulseresponse_x$, is the Riesz representation of $\Aop \delta_x^*$. 
%From \eqref{eq:appendix_impulse_response} and the definition of the Riesz representation, we have $\impulseresponse_x = A(~\cdot~,x)$. That is, $\impulseresponse_x$ is the function $y \mapsto A(y,x)$.
